\documentclass[11pt,a4paper]{article}

% ----------------------------------------------------------------------
% Packages
% ----------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage[hidelinks]{hyperref}

% ----------------------------------------------------------------------
% Colors and code style
% ----------------------------------------------------------------------
\definecolor{dauphineblue}{RGB}{0,81,186}
\definecolor{codebg}{RGB}{245,245,245}
\definecolor{codekw}{RGB}{0,81,186}
\definecolor{codecomment}{RGB}{90,110,90}

\lstset{
    basicstyle=\ttfamily\small,
    backgroundcolor=\color{codebg},
    keywordstyle=\color{codekw}\bfseries,
    commentstyle=\color{codecomment}\itshape,
    stringstyle=\color{red!60!black},
    numbers=left,
    numberstyle=\tiny\color{gray},
    breaklines=true,
    showstringspaces=false,
    frame=single,
    rulecolor=\color{gray!40},
    framesep=4pt,
    aboveskip=8pt,
    belowskip=6pt,
    language=Java,
}

% Pseudo-code environment, plain text, no language keywords.
\lstdefinestyle{pseudo}{
    basicstyle=\ttfamily\small,
    backgroundcolor=\color{codebg},
    numbers=none,
    keywordstyle=\color{codekw}\bfseries,
    morekeywords={if,then,else,while,for,return,each,do,push,pop,add,not,and},
    frame=single,
    rulecolor=\color{gray!40},
}

% ----------------------------------------------------------------------
% Header and footer
% ----------------------------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\lhead{\small Artificial Intelligence and Reasoning}
\rhead{\small Lab 1: Rubik's Cube Solver}
\cfoot{\small \thepage}

\setlength{\parskip}{0.4em}
\setlength{\parindent}{0pt}

% ----------------------------------------------------------------------
\begin{document}

% ======================================================================
% TITLE PAGE (not counted in the 12 pages)
% ======================================================================
\begin{titlepage}
\centering
\vspace*{2cm}

{\Large \textbf{Universite Paris Dauphine, PSL}}\\[0.3cm]
{\large Master 1 MIAGE}\\[2.5cm]

{\color{dauphineblue}\rule{\linewidth}{1.2pt}}\\[0.4cm]
{\huge \textbf{Solving the Rubik's Cube}}\\[0.5cm]
{\LARGE with the A* Search Algorithm}\\[0.4cm]
{\color{dauphineblue}\rule{\linewidth}{1.2pt}}\\[1.5cm]

{\large \textit{Course: Artificial Intelligence and Reasoning}}\\[0.3cm]
{\large Lab 1 Project Report}\\[2.5cm]

{\large \textbf{Authors}}\\[0.3cm]
{\large Mathias CHEBBAH}\\[0.15cm]
{\large Lamine BETRAOUI}\\[0.15cm]
{\large Bouna SALL}\\[2cm]

\vfill
{\large June 2026}

\end{titlepage}

% ======================================================================
% PAGE 1
% ======================================================================
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

This report presents a program that solves the Rubik's Cube. We model the cube
as a search problem and we solve it with the A* algorithm seen in Lecture 2.
We first use a uniform cost search, then we add two admissible heuristics that
guide the search. The first heuristic relaxes the problem so that each sticker
moves on its own. The second heuristic relaxes it so that each piece moves on
its own. We measure how scrambled a cube can be while still being solved in a
reasonable time. The results confirm the course statement: a good heuristic
gives large savings, and A* runs out of memory long before it runs out of time.

\tableofcontents

\vspace{1cm}

% ----------------------------------------------------------------------
\section{Introduction}

A Rubik's Cube is a small cube made of nine stickers on each of its six faces.
Each face can turn, which mixes the colors. The cube is solved when every face
shows a single color. Our goal is to write the "solve" button of a cube
simulator: given any mixed configuration, the program must return a sequence of
moves that brings the cube back to the solved state.

This problem fits the search framework of the course. A configuration is a
state, a quarter turn is an action, and the solved cube is the goal. Because the
moves all cost one, the shortest sequence of moves is the optimal solution. We
therefore use the search methods of Lecture 2, and in particular the A*
algorithm, which finds an optimal solution when its heuristic is admissible.

The report is organized as follows. Section 2 states the problem with the five
components of a search problem. Section 3 describes the classes of our program.
Section 4 explains the A* algorithm and our implementation. Section 5 presents
the two heuristics and shows that they are admissible. Section 6 reports our
experiments. Section 7 concludes.

\end{document}
